An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-20 EconGrowth-R-Functions.Rnw
Implemented a 9-panel lattice graph for the triangle plots with function CIvsParamLattice. Need to work on the formatting of the graphs, but this is now in there.

########################
# Creates a lattice plot that has the size of confidence intervals on the vertical axis and parameter
# values on the horizontal axis.
# At this point, this function is NOT a general-purpose function, as the number of permutations
# of model, parameter, energy type, and factor is too varied to be able to turn into a general-purpose 
# graph with little time investment at this point.
# This function makes a lattice plot with the following panels (in the arrangement shown)
#
# gammaCDeq   gammaCDex    gammaCDeu
# deltaCESeq  deltaCESex   deltaCESeu
# sigmaCESeq  sigmaCESex   sigmaCESeu
#
# Parameters and models (gamma for CDe and delta and sigma for CESe) are in rows and energyTypes (q, x, and u) 
# are in columns.
##
CIvsParamLattice <- function(descriptors){
  # Build a data.frame that has all the necessary models
  gammaCDeqDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="Q")
  gammaCDexDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="X")
  gammaCDeuDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="U")
  deltaCESeqDF <- CIvsParamDF(model="CESe", param="delta", energyType="Q")
  deltaCESexDF <- CIvsParamDF(model="CESe", param="delta", energyType="X")
  deltaCESeuDF <- CIvsParamDF(model="CESe", param="delta", energyType="U")
  sigmaCESeqDF <- CIvsParamDF(model="CESe", param="sigma", energyType="Q")
  sigmaCESexDF <- CIvsParamDF(model="CESe", param="sigma", energyType="X")
  sigmaCESeuDF <- CIvsParamDF(model="CESe", param="sigma", energyType="U")
  # Change the name of the first columns (the ones that contain the parameter of interest to us) to "param".
  # Doing this allows us to combine the individual data frames into one large data frame.
  colnames(gammaCDeqDF)[1]  <- "param"
  colnames(gammaCDexDF)[1]  <- "param"
  colnames(gammaCDeuDF)[1]  <- "param"
  colnames(deltaCESeqDF)[1] <- "param"
  colnames(deltaCESexDF)[1] <- "param"
  colnames(deltaCESeuDF)[1] <- "param"
  colnames(sigmaCESeqDF)[1] <- "param"
  colnames(sigmaCESexDF)[1] <- "param"
  colnames(sigmaCESeuDF)[1] <- "param"
  # Create one big data.frame with all of the data.
  data <- rbind(gammaCDeqDF,  gammaCDexDF,  gammaCDeuDF, 
                deltaCESeqDF, deltaCESexDF, deltaCESeuDF, 
                sigmaCESeqDF, sigmaCESexDF, sigmaCESeuDF)
print(data)
  # Now make the graph.
}
@

>>>>

########################
# Creates a lattice plot that has the size of confidence intervals on the vertical axis and parameter
# values on the horizontal axis.
# At this point, this function is NOT a general-purpose function, as the number of permutations
# of model, parameter, energy type, and factor is too varied to be able to turn into a general-purpose 
# graph with little time investment at this point.
# This function makes a lattice plot with the following panels (in the arrangement shown)
#
# gammaCDeq   gammaCDex    gammaCDeu
# deltaCESeq  deltaCESex   deltaCESeu
# sigmaCESeq  sigmaCESex   sigmaCESeu
#
# Parameters and models (gamma for CDe and delta and sigma for CESe) are in rows and energyTypes (q, x, and u) 
# are in columns.
##
CIvsParamLattice <- function(descriptors){
  # Build a data.frame that has all the necessary models
  gammaCDeqDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="Q")
  gammaCDexDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="X")
  gammaCDeuDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="U")
  deltaCESeqDF <- CIvsParamDF(model="CESe", param="delta", energyType="Q")
  deltaCESexDF <- CIvsParamDF(model="CESe", param="delta", energyType="X")
  deltaCESeuDF <- CIvsParamDF(model="CESe", param="delta", energyType="U")
  sigmaCESeqDF <- CIvsParamDF(model="CESe", param="sigma", energyType="Q")
  sigmaCESexDF <- CIvsParamDF(model="CESe", param="sigma", energyType="X")
  sigmaCESeuDF <- CIvsParamDF(model="CESe", param="sigma", energyType="U")
  # Change the name of the first columns (the ones that contain the parameter of interest to us) to "param".
  # Doing this allows us to combine the individual data frames into one large data frame.
  colnames(gammaCDeqDF)[1]  <- "param"
  colnames(gammaCDexDF)[1]  <- "param"
  colnames(gammaCDeuDF)[1]  <- "param"
  colnames(deltaCESeqDF)[1] <- "param"
  colnames(deltaCESexDF)[1] <- "param"
  colnames(deltaCESeuDF)[1] <- "param"
  colnames(sigmaCESeqDF)[1] <- "param"
  colnames(sigmaCESexDF)[1] <- "param"
  colnames(sigmaCESeuDF)[1] <- "param"
  # Create one big data.frame with all of the data.
  data <- rbind(gammaCDeqDF,  gammaCDexDF,  gammaCDeuDF, 
                deltaCESeqDF, deltaCESexDF, deltaCESeuDF, 
                sigmaCESeqDF, sigmaCESexDF, sigmaCESeuDF)
  # Now make the graph.
  # Need to use the indices in the following code, because the column labels will be different for each type
  # of model. In other words, if we're doing CESe with Q and plotting sigma, the data.frame will come 
  # back with column names of "sigma" and "CI" on the first and second column, respectively. 
  # plot <-  xyplot(data$CI ~ data$sigma, ...)
  # would break if we, instead, wanted CESe with Q and plotting delta.
  # So, instead, we use the column indices to pick off the correct variables.
  # data[ , 1] contains the the parameter; 
  # data[ , 2] contains the CI width; 
  # data[ , 3] contains the descriptor for the type of graph it is.
  plot <- xyplot(data[ , 2] ~ data[ , 1] | data[ , 3], 
#                  xlab=list(label=xLabel),
#                  ylab=list(label=yLabel),
#                  scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
#                              tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
#                              x=list(at=atX),
#                              y=list(at=atY)
#                              ), 
#                  xlim=xLimits, #x axis limits
#                  ylim=yLimits, #y axis limits
                 panel = function(x, y){
                   ltext(x=x, y=y, labels=data[ , 4]) # Picks up the 4th column containing the country abbreviations.
                 })
  return(plot)
}
@
